Comparing shared and distributed memory algorithms: A case study on Matrix Transposition and Symmetry Check\\

### 2025-01-19 latex/paper2.tex
latex: updated names in figures

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_base.pdf"}
	\caption{matTransposeMPI average time over matrix size}
	\label{fig:transpose_mpi_base}
\end{figure}

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_block_base.pdf"}
	\caption{matTransposeMPIBlock average time over matrix size}
	\label{fig:transpose_mpi_block}
\end{figure}

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_speedup.pdf"}
	\caption{matTransposeMPI speedup measurements}
	\label{fig:transpose_mpi_speedup}
\end{figure}

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_block_speedup.pdf"}
	\caption{matTransposeMPIBlock speedup measurements}
	\label{fig:transpose_mpi_block_speedup}
\end{figure}

@@

\iffalse
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_weak_scaling.pdf"}
	\caption{matTransposeMPI weak scaling measurements}
	\label{fig:transpose_mpi_weak_scaling}
\end{figure}
\fi

\iffalse
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_block_bandwidth.pdf"}
	\caption{matTransposeMPIBlock bandwidth measurements}
	\label{fig:transpose_mpi_block_bandwidth}
\end{figure}
\fi

\iffalse
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_block_weak_scaling.pdf"}
	\caption{matTransposeMPIBlock weak scaling measurements}
	\label{fig:transpose_mpi_block_weak_scaling}
\end{figure}
\fi

>>>>

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_base.pdf"}
	\caption{matTransposeMPI average time over matrix size of multiple number of processes}
	\label{fig:transpose_mpi_base}
\end{figure}

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_block_base.pdf"}
	\caption{matTransposeMPIBlock average time over matrix size of multiple number of processes}
	\label{fig:transpose_mpi_block}
\end{figure}

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_speedup.pdf"}
	\caption{matTransposeMPI speedup measurements of multiple number of processes}
	\label{fig:transpose_mpi_speedup}
\end{figure}

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_block_speedup.pdf"}
	\caption{matTransposeMPIBlock speedup measurements of multiple number of processes}
	\label{fig:transpose_mpi_block_speedup}
\end{figure}

@@

\iffalse
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_weak_scaling.pdf"}
	\caption{matTransposeMPI weak scaling measurements of multiple number of processes}
	\label{fig:transpose_mpi_weak_scaling}
\end{figure}
\fi

\iffalse
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_block_bandwidth.pdf"}
	\caption{matTransposeMPIBlock bandwidth measurements of multiple number of processes}
	\label{fig:transpose_mpi_block_bandwidth}
\end{figure}
\fi

\iffalse
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.44\textwidth]{"../benchmarks/plotting/images/matTransposeMPI_block_weak_scaling.pdf"}
	\caption{matTransposeMPIBlock weak scaling measurements of multiple number of processes}
	\label{fig:transpose_mpi_block_weak_scaling}
\end{figure}
\fi
